lfl: Linguistic Fuzzy Logic in \R{} -- Part I

### 2021-02-06 chunks/chunk-pbld2.tex
Disabled prompt
Shortening outputs

\begin{Schunk}
% --begin: "pbld2"
\begin{Sinput}
R> uptakeContext <- ctx3(7, 28.3, 46)
R> d <- lcut(CO2, context = list(uptake = uptakeContext))
R> colnames(d)
\end{Sinput}
\begin{Soutput}
 [1] "Plant=Qn1"            "Plant=Qn2"           
 [3] "Plant=Qn3"            "Plant=Qc1"           
 [5] "Plant=Qc3"            "Plant=Qc2"           
 [7] "Plant=Mn3"            "Plant=Mn2"           
 [9] "Plant=Mn1"            "Plant=Mc2"           
[11] "Plant=Mc3"            "Plant=Mc1"           
[13] "Type=Quebec"          "Type=Mississippi"    
[15] "Treatment=nonchilled" "Treatment=chilled"   
[17] "ex.sm.conc"           "si.sm.conc"          
[19] "ve.sm.conc"           "sm.conc"             
[21] "ml.sm.conc"           "ro.sm.conc"          
[23] "qr.sm.conc"           "vr.sm.conc"          
[25] "ty.me.conc"           "me.conc"             
[27] "ml.me.conc"           "ro.me.conc"          
[29] "qr.me.conc"           "vr.me.conc"          
[31] "ex.bi.conc"           "si.bi.conc"          
[33] "ve.bi.conc"           "bi.conc"             
[35] "ml.bi.conc"           "ro.bi.conc"          
[37] "qr.bi.conc"           "vr.bi.conc"          
[39] "ex.sm.uptake"         "si.sm.uptake"        
[41] "ve.sm.uptake"         "sm.uptake"           
[43] "ml.sm.uptake"         "ro.sm.uptake"        
[45] "qr.sm.uptake"         "vr.sm.uptake"        
[47] "ty.me.uptake"         "me.uptake"           
[49] "ml.me.uptake"         "ro.me.uptake"        
[51] "qr.me.uptake"         "vr.me.uptake"        
[53] "ex.bi.uptake"         "si.bi.uptake"        
[55] "ve.bi.uptake"         "bi.uptake"           
[57] "ml.bi.uptake"         "ro.bi.uptake"        
[59] "qr.bi.uptake"         "vr.bi.uptake"        
\end{Soutput}
%
% --end: "pbld2"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "pbld2"
\begin{Sinput}
R> uptakeContext <- ctx3(7, 28.3, 46)
R> d <- lcut(CO2, context = list(uptake = uptakeContext))
R> colnames(d)
\end{Sinput}
\begin{Soutput}
 [1] "Plant=Qn1"            "Plant=Qn2"            "Plant=Qn3"           
 [4] "Plant=Qc1"            "Plant=Qc3"            "Plant=Qc2"           
 [7] "Plant=Mn3"            "Plant=Mn2"            "Plant=Mn1"           
[10] "Plant=Mc2"            "Plant=Mc3"            "Plant=Mc1"           
[13] "Type=Quebec"          "Type=Mississippi"     "Treatment=nonchilled"
[16] "Treatment=chilled"    "ex.sm.conc"           "si.sm.conc"          
[19] "ve.sm.conc"           "sm.conc"              "ml.sm.conc"          
[22] "ro.sm.conc"           "qr.sm.conc"           "vr.sm.conc"          
[25] "ty.me.conc"           "me.conc"              "ml.me.conc"          
[28] "ro.me.conc"           "qr.me.conc"           "vr.me.conc"          
[31] "ex.bi.conc"           "si.bi.conc"           "ve.bi.conc"          
[34] "bi.conc"              "ml.bi.conc"           "ro.bi.conc"          
[37] "qr.bi.conc"           "vr.bi.conc"           "ex.sm.uptake"        
[40] "si.sm.uptake"         "ve.sm.uptake"         "sm.uptake"           
[43] "ml.sm.uptake"         "ro.sm.uptake"         "qr.sm.uptake"        
[46] "vr.sm.uptake"         "ty.me.uptake"         "me.uptake"           
[49] "ml.me.uptake"         "ro.me.uptake"         "qr.me.uptake"        
[52] "vr.me.uptake"         "ex.bi.uptake"         "si.bi.uptake"        
[55] "ve.bi.uptake"         "bi.uptake"            "ml.bi.uptake"        
[58] "ro.bi.uptake"         "qr.bi.uptake"         "vr.bi.uptake"        
\end{Soutput}
%
% --end: "pbld2"
\end{Schunk}
